Intentional stocking undermines ecological stability

### 2022-02-25 rmd/manuscript.Rmd
edit: manuscript

Competition is a likely mechanism, as our theory assumes. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003]. Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities. As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Masato Yamamichi for helpful discussion on this manuscript. Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.

>>>>

Competition is a likely mechanism, as our theory assumes. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003]. Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015; @hasegawaPulsedSuppliesSmall2022]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities. As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Genki Sahashi and Masato Yamamichi for helpful discussion on this manuscript. Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
